### 2020-05-10 thesis_template/3_Body/model/drop_ref_rc.tex
conclusion done
done

In this experiment, CustomerBorrowed and CustomerRc are used to see difference of dropping time among reference and Rc. 
In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
The dropping of objects deletes references or Rcs used for fields of the objects. However, it does not deallocate values to which they are pointing. 
Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
We generated 1, 1.5, 2, 2.5, 3, 3.5 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.

\subsection{Result}
Figure\ref{fig:rc_ref} shows comparison of runtime dropping CustomerBorrowed and CustomerRc objects. 
The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
The runtime of dropping CustomerBorrowed is about 60 times faster than dropping CustomerRc.

>>>>

In this experiment, CustomerBorrowed and CustomerRc are used to see difference of dropping time among reference and Rc. 
In the CustomerRc and OrderRc struct, all fields take Rc (Rc$<$T$>$). Similarly to the experiment in the last section, 
sets of integer, float, and String vector are created and their elements are borrowed or reference counted to create CustomerBorrowed or CustomerRc objects.
The dropping of objects deletes references or Rcs used for fields of the objects. However, it does not deallocate values to which they are pointing. 
Therefore, the evaluated runtime of dropping objects only consists of dropping time of reference or Rc, but deallocation time.
We generated 10, 20, 30, and 40 million of CustomerBorrowed and CustomerRc objects and performed drop one by one.

\subsection{Result}
Figure\ref{fig:rc_ref} shows comparison of runtime dropping CustomerBorrowed and CustomerRc objects. 
The result shows significant difference of dropping time among the two objects; deletion of CustomerRc is much slower than CustomerBorrowed. 
The runtime of dropping CustomerBorrowed is about 60 times faster than dropping CustomerRc. 
The memory usage for algorithms with 40 million of Customer objects are about 26G bytes for both CustomerRc and CustomerBorrowed.
